The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications

### 2017-04-20 paper.tex
Added stub for Peter.
Started section on time-bin qubits.

@@

\subsection{State preparation}
\sihui{Cat state--Schoelkopf group}

@@

@@

>>>>

\subsubsection{Time-bins}
Time-bin qubits is quantum information that is encoded on the time-of-arrival of single photons. It was first conceived for a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}. If the photon passes through the shorter (longer) path, then it will arrive at the output port in an ``early" (``late") time bin. Thus, photon will exit the interferometer in a state that is a superposition of these two states. Owing to difficulties in implementing qubit operations in this basis, it was at that time mostly used for demonstrating quantum communication over long distance \cite{bib:Thew02,bib:Marcikic04}. With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operations, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}. At the same time, an ultrafast measurement technique for recovering time-bin qubits was also demonstrated \cite{bib:Donohue2013}.

@@

\subsection{State preparation}

@@

\sihui{ SPDC, quantum-dot micropillar sources}

@@

\sihui{Peter to fill this in}
\cite{bib:Motes14}
